The transition redshift as a probe of reionization

### 2019-08-12 paper/ms.tex
Modify plot placements
Fix previous commit
Small updates

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. Beane and K. Moriwaki]{
Angus Beane$^{1}$\thanks{E-mail: angus.beane@cfa.harvard.edu}
and Kana Moriwaki$^{2}$\thanks{E-mail: kana.moriwaki@utap.phy.s.u-tokyo.ac.jp}
\\
% List of institutions
$^{1}$Center for Astrophysics {\normalfont |} Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{2}$Department of Physics, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan
% $^{2}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, NY 10010, USA\\
% $^{3}$Department of Physics \& Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA
}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/ztran_vs_k/ztran_vs_k.pdf}
\caption{The transition redshift ($\zst$) as defined by cross-correlating with the
density field (solid lines) and all resolved halos (dashed lines, $M\gtrsim
5\times10^9\,\Msun$), for our three different EoR models (\hot{}, \fid{}, and
\cold{}). We see that \zst{} is only a mild function of $k$ for the three
models, with slightly stronger dependence as the heating of the model
decreases. The most dependence comes in the \cold{} model, where \zst{}
changes by $\sim7\,\%$ from $k=0.1$ to $0.6\,\hoverMpc$. {\bf Some words for
why cold and fid cut off at some k}}
\label{fig:ztran_vs_k}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{../plots/ztran_vs_Mcut/ztran_vs_Mcut.pdf}
\caption{The transition redshift (\zst) as defined by cross-correlating with the halo field for our three different EoR models (\hot{}, \fid{}, and
\cold{}) as a function of the cut-off mass. The cross-correlation is only made
between the 21~cm field and all halos with masses $M>M_{\text{cut}}$. One can
see that for the \fid{} and \cold{} models, \zst{} is only mildly a function
of $M_{\text{cut}}$ below a certain cut-off mass ($\sim10^{10.5}\,\Msun$ in
both models). In other words, as long as a galaxy survey is deep enough so as
to resolve a sufficient number of galaxies, the \zst{} is not dependent on the
depth of the survey. The \hot{} model shows more dependence, but this may be
due to sampling noise due to the smaller number of such halos at the higher
\zst{} typical for the \hot{} model.}
\end{figure}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. Beane, K. Moriwaki, ...]{
Angus Beane$^{1}$\thanks{E-mail: angus.beane@cfa.harvard.edu},
Kana Moriwaki$^{2}$,
and others
\\
% List of institutions
$^{1}$Center for Astrophysics {\normalfont |} Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{2}$Department of Physics, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan
% $^{2}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, NY 10010, USA\\
% $^{3}$Department of Physics \& Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA
}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{plots/ztran_vs_k.pdf}
\caption{The transition redshift ($\zst$) as defined by cross-correlating with the
density field (solid lines) and all resolved halos (dashed lines, $M\gtrsim
5\times10^9\,\Msun$), for our three different EoR models (\hot{}, \fid{}, and
\cold{}). We see that \zst{} is only a mild function of $k$ for the three
models, with slightly stronger dependence as the heating of the model
decreases. The most dependence comes in the \cold{} model, where \zst{}
changes by $\sim7\,\%$ from $k=0.1$ to $0.6\,\hoverMpc$. {\bf Some words for
why cold and fid cut off at some k}}
\label{fig:ztran_vs_k}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{plots/ztran_vs_Mcut.pdf}
\caption{The transition redshift (\zst) as defined by cross-correlating with the halo field for our three different EoR models (\hot{}, \fid{}, and
\cold{}) as a function of the cut-off mass. The cross-correlation is only made
between the 21~cm field and all halos with masses $M>M_{\text{cut}}$. One can
see that for the \fid{} and \cold{} models, \zst{} is only mildly a function
of $M_{\text{cut}}$ below a certain cut-off mass ($\sim10^{10.5}\,\Msun$ in
both models). In other words, as long as a galaxy survey is deep enough so as
to resolve a sufficient number of galaxies, the \zst{} is not dependent on the
depth of the survey. The \hot{} model shows more dependence, but this may be
due to sampling noise due to the smaller number of such halos at the higher
\zst{} typical for the \hot{} model.}
\end{figure}
